### 2019-03-18 papers/journal/encoding.tex
Update to bmc

In the $\fbmc$ encoding, the label of edges and nodes are represented as an array of bit vector of size $M$. 
%
For example, the bit vector \texttt{bvEdge}$[i][j][q]$ is the label is the $q$th edge between node $i$ and $j$.
% with each bit corresponding to the presence or absence of the molecule. 
%
%In the $\fbmc$ encoding, variables are represented as an array of bit vectors of size $M$. 
%
%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
%%
%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
%\begin{align*}
%graph [i] [j] = x.
%\end{align*}
%
%For example, every edge is represented as a bit vector of size $M$ with each bit corresponding to the presence or absence of the molecule. 
%
%Bit vector \texttt{bvEdge}$[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
%
%The index of the bit vector implicitly determines the corresponding molecule we are referring to in the edge.
%

%The molecule set is divided into Q and R-SNAREs. 
%
%For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
%An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
%
%Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
%
%Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
%
%For example, the variable \texttt{bvEdge}[1][2][1] = 1001, represents the first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
%
%Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
%
%We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
%

The value of the bit vector describes the presence of corresponding molecules at the particular location. 
%
For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
For example, the variable \texttt{bvEdge}[0][2][1] = 1001, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 1 and node 2.

In order to specify the stability condition, we use a combination of enumeration and nondeterminism.
%
Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific $m$ if it exists. 
%
We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
%

\subsubsection{Constraints for stability condition}
%
We use \texttt{NOracle} to represent the required path to encode the stability condition in VTS.
%
A naive implementation is shown in~\ref{eq:reachbmc1} where \texttt{NOracle}$(m, i, j, w)$ represent the presence of a $m$-$path$ from node $i$ to node $j$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and01
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
It performs enumeration of every $m$-$path$, $m$-${paths}_i^j$, of at most $w$ length. 
%
Starting with exploring $m$-${paths}_i^j$ of length 1, a direct edge between $i$ and $j$ with molecule $m$ present on it, until every $m$-${paths}_i^j$ of length $w-1$ is explored.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.

@@

\begin{align}
\texttt{NOracle}(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} | {m-path}_i^j | = l
  \tag{S1}\label{eq:reachbmc1}
\end{align}

We encode stability using \texttt{NOracle}. If there is an $m$-edge between node $i$ and $j$, there has to be a $m$-$path_i^j$ from $j$ to $i$ of maximum $w$ length.
%
The expression (\texttt{bv} $\unrhd$ $m$) extracts the $m^{th}$ bit of the bitvector \texttt{bv}.

\begin{align}
	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) := 1) \limplies \texttt{NOracle}(m, j, i, w)
  \tag{S2}\label{eq:reachbmc2}
\end{align}

>>>>

In the $\fbmc$ encoding, the label of edges and nodes are represented as an array of bit vector of size $M$. 
%
For example, the bit vector \texttt{bvEdge}$[i][j][q]$ is the label is the $q$th edge between node $i$ and $j$.

% with each bit corresponding to the presence or absence of the molecule. 
%
%In the $\fbmc$ encoding, variables are represented as an array of bit vectors of size $M$. 
%
%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
%%
%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
%\begin{align*}
%graph [i] [j] = x.
%\end{align*}
%
%For example, every edge is represented as a bit vector of size $M$ with each bit corresponding to the presence or absence of the molecule. 
%
%Bit vector \texttt{bvEdge}$[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
%
%The index of the bit vector implicitly determines the corresponding molecule we are referring to in the edge.
% 
%The molecule set is divided into Q and R-SNAREs. 
%
%For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
%An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
%
%Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
%
%Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
%
%For example, the variable \texttt{bvEdge}[1][2][1] = 1001, represents the first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
%
%Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
%
%We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
%
%
The value of the bit vector describe the presence of the corresponding molecules at that particular location. 
%
For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
For example, the variable \texttt{bvEdge}[0][2][1] = $1001$, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 1 and node 2.

To specify the stability condition, we use a combination of enumeration and nondeterminism.
%
The encoding here presents a simpler version of the implementation. 
%Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific $m$ if it exists. 
%
%We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
%

\subsubsection{Constraints for stability condition}
%
A path between node $i$ and $j$ in the graph is a $m$-$path_{ij}$, if there exists a path with molecule $m$ present on edges along the path between node $i$ and $j$.
%
%We use {\npath} to represent the required path to encode the stability condition in VTS.
%
%A naive implementation is shown in~\ref{eq:reachbmc1} where 
We use {\npath}$(m, i, j, w)$ to represent the presence of a $m$-$path_{ij}$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and01
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
The~\ref{eq:reachbmc1} performs enumeration of every $m$-$path_{ij}$ of at most $w$ length. 
%
Starting with exploring $m$-${paths}_{ij}$ of length 1, a direct edge between $i$ and $j$ with molecule $m$ present on it, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.

@@

\begin{align}
\npath(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} (\texttt{Length} (m-path_{ij}) == l)
  \tag{S1}\label{eq:reachbmc1}
\end{align}

We encode stability using \npath. For every edge with $m^{th}$ molecule present between node $i$ and $j$ then there exists a $m$-$path_{ji}$ of maximum $w$ length.
%
The expression (\texttt{bv} $\unrhd$ $m$) extracts the $m^{th}$ bit of the bitvector \texttt{bv}.

\begin{align}
	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) := 1) \limplies \npath(m, j, i, w)
  \tag{S2}\label{eq:reachbmc2}
\end{align}
